rmac
========================================================

#### Comparison of `FMAC` and `RMAC` for interrater agreement <br>
rmac method is insensitive to changes in marginal probabilities--Fay says this is an advantage to his method

### Example 1: from paper; swapping cells [1,3] and [3,1]

```{r tidy = FALSE}
require(rmac, quietly = TRUE)
options(width=60)
#The Multiple Sclerosis Diagnoses Example (from Fay 2005)
#the original data
msd1<- as.table(matrix(data = c(38,5,0,1,
                                33,11,3,0,
                                10,14,5,6,
                                3,7,3,10), 4,4, byrow = TRUE))
msd1
# calculate the FMAC and RMAC
wkappa(msd1, method = 'fmac')$estimate
wkappa(msd1, method = 'rmac')$estimate
# the data with cell counts (1,3) and (3,1) reversed
msd2<- as.table(matrix(data = c(38,5,10,1,
                                33,11,3,0,
                                0,14,5,6,
                                3,7,3,10), 4,4, byrow = TRUE))
msd2
# calculate the FMAC and RMAC
wkappa(msd2, method = 'fmac')$estimate
wkappa(msd2, method = 'rmac')$estimate
```

<br>
<br>

#### FMAC increases by 0.022 <br>
#### RMAC is unaffected

<br>
<br>

### Example 2: Balanced marginals

```{r tidy = FALSE}
require(rmac, quietly = TRUE)
options(width=60)
msd1<- as.table(matrix(data = c(38,19,5,2,
                                19,11,9,3,
                                5,8,5,5,
                                2,4,4,10), 4,4, byrow = TRUE))
msd1
# calculate the FMAC and RMAC
wkappa(msd1, method = 'fmac')$estimate
wkappa(msd1, method = 'rmac')$estimate
```

<br>
<br>

#### Both methods are equivalent

<br>
<br>

### Example 3: Extreme imbalance in marginals

```{r tidy = FALSE}
# upper triangular
msd1<- as.table(matrix(data = c(38,38,10,4,
                                0,11,17,7,
                                0,0,5,9,
                                0,0,0,10), 4,4, byrow = TRUE))
msd1
# calculate the FMAC and RMAC
wkappa(msd1, method = 'fmac')$estimate
wkappa(msd1, method = 'rmac')$estimate
```

<br>
<br>

#### FMAC increases by 0.016 <br>
#### RMAC is unaffected
